%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MASTER CV – TAILORING GUIDE (INTERNAL, DO NOT COMPILE)
%
% Purpose:
%   This file is a modular "master CV" used to generate
%   position-specific CVs and resumes with the help of ChatGPT.
%   It is NOT intended to be submitted as-is.
%
% How to use with ChatGPT:
%   1. Provide THIS file (master.tex) and the job ad to ChatGPT.
%   2. Ask ChatGPT to:
%        - Select and edit bullets that best match the job ad.
%        - Remove irrelevant subsections and bullets.
%        - Output a final LaTeX file with only the tailored content.
%
% Role structure:
%   • Under each role, bullets are grouped into focus subsections
%     (e.g., "Material Simulation and Analysis",
%            "Software Development and Automation",
%            "High-Performance Computing and Workflow Acceleration",
%            "Leadership, Mentorship, and Community Engagement").
%   • These are MENU CATEGORIES for tailoring and MUST NOT appear
%     in the final submitted CV.
%
%   In the FINAL CV:
%     - KEEP only the main role lines, e.g.
%         \textbf{Postdoctoral Researcher}, University of South Florida
%     - REMOVE all focus subsection headings such as:
%         \textbf{Material Simulation and Analysis}
%         \textbf{Software Development and Automation}
%
% Length targets (FINAL CV):
%   • Industry / national lab roles: 1–2 pages max.
%   • Academic research/teaching roles: 3–4 pages max (only if needed).
%
% Bullet COUNT per role (FINAL CV):
%   • Postdoc + PhD roles: 4–7 bullets each.
%   • Earlier roles (AUS MS, undergraduate): 2–3 bullets each.
%      Prioritize bullets that directly match REQUIRED or PREFERRED
%      qualifications in the job ad.
%
% Bullet LENGTH rules (IMPORTANT):
%   • ALL bullets in the final PDF must be concise, refined, and
%     easy to scan. NO wall-of-text bullets.
%   • For the first 3 bullets under the Postdoc and PhD roles:
%       - Allow up to ~2 lines (max) in the compiled PDF.
%       - Each bullet should still express ONE clear idea
%         (Action → Method → Impact), not a paragraph.
%   • For ALL other bullets (including AUS Masters, leadership section, and
%     later bullets in each role):
%       - STRICT limit: 1 line in the compiled PDF.
%       - If needed, REMOVE clauses instead of wrapping to a 2nd line.
%
%   • When compressing:
%       - Prefer merging or removing secondary details rather than
%         stacking multiple clauses.
%       - Drop redundant context if the same idea appears elsewhere.
%
% Numbers and notation:
%   • In the FINAL CV, prefer DIGITS over spelled-out numbers to
%     improve scanability, e.g.:
%       - "10+ TB", "5–7 bullets", "3+ years", "500+ members".
%   • Keep units tight and standard (TB, GB, GPU, node, %, etc.).
%
% Keyword and audience adaptation:
%   • Rephrase bullets to inject key terms from the job ad
%     (skills, tools, responsibilities, impact) while keeping
%     factual accuracy.
%   • For industry/HPC/software roles, prioritize bullets that
%     emphasize:
%       - Software Development
%       - HPC / GPU / profiling / performance
%       - Automation, pipelines, tooling
%       - Cross-functional collaboration / enabling others
%   • For more academic-facing applications, prioritize:
%       - Molecular Simulation / Polymer Physics
%       - Structure–property relationships
%       - Publications, invited talks, mentoring
%
% General editing guidance for the FINAL CV:
%   • Do NOT invent new experiences; only recombine and lightly
%     rephrase what exists in this master.
%   • Remove entire bullets or subsections if they are not clearly
%     relevant to the target job ad.
%   • Prefer fewer, sharper bullets over many repetitive ones.
%   • ALWAYS check that the resulting bullets obey:
%       - Page limit
%       - Bullet count per role
%       - Bullet length rules above.
%
% Output:
%   • Respond in LaTeX.
%   • Ensure this Tailoring Guide remains commented out and does
%     NOT appear in the compiled PDF.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,12pt]{article}
\usepackage[margin=1.00in, top=0.7in, headsep=20pt]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{fontawesome}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
}

% Font
\usepackage[T1]{fontenc}
\usepackage[sc]{mathpazo}

\usepackage[backend=biber,sorting=mysort,style=numeric-comp,defernumbers,maxbibnames=20]{biblatex}
\addbibresource[label=articles]{articles.bib}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
 % fix header
 \defbibheading{fix}[\refname]{\section*{#1}}
 

\AtBeginBibliography{\small}

  % This is the sorting scheme for the CV
  \DeclareSortingScheme{mysort}{
    \sort[direction=descending]{
      \field{year}
    }
    \sort[direction=descending]{
      \field[padside=left,padwidth=2,padchar=0]{month}
      \literal{00}
    }
  }

  % Use this for reversing the numbers (count down) in the bibliography
  % Count total number of entries in each refsection
  \AtDataInput{%
  \csnumgdef{entrycount:\therefsection}{%
  \csuse{entrycount:\therefsection}+1}}

  % Print the labelnumber as the total number of entries in the
  % current refsection, minus the actual labelnumber, plus one
  \DeclareFieldFormat{labelnumber}{\mkbibdesc{#1}}    
  \newrobustcmd*{\mkbibdesc}[1]{%
  \number\numexpr\csuse{entrycount:\therefsection}+1-#1\relax}

% Custom sections
\usepackage[]{titlesec}
\titleformat{\section}{
  \rmfamily\mdseries\Large\bfseries
  }{}{}{}[\vspace{0.1ex}\titlerule]
\titlespacing*{\section}{0ex}{3ex}{0.8ex}
\titlespacing*{\therefsection}{0ex}{3ex}{0.8ex}
\titlespacing*{\refsection}{0ex}{3ex}{0.8ex}

\newlist{tabitemize}{itemize}{1}
%\setlist[tabitemize]{label=\textbullet,nosep,align=parleft,leftmargin=*,}
\setlist[tabitemize]{label=\textbullet,itemsep=1pt,align=parleft,leftmargin=*,}

%% Customize page headers
%\pagestyle{myheadings}
%\markright{\name}
%\thispagestyle{empty}
\usepackage[]{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
%\fancyhead[RO,LE]{Pierre Kawak, Ph.D.}
\fancyfoot{}
\fancyfoot[LO,CE]{\thepage}
\fancyfoot[RO,LE]{Pierre Kawak, Ph.D.}
\begin{document}

\begin{center}
  {\LARGE \textbf{Pierre Kawak, Ph.D.}}\\ \vspace{2mm}
  Open to relocation \quad Eligible to work in the U.S. \quad No sponsorship needed \\ \vspace{1.5mm}
  \faPhone\ (801) 762-7999 \quad \faEnvelope\ \href{mailto:pskawak@gmail.com}{pskawak@gmail.com} \quad \faLink\ \href{https://linktr.ee/pkawak}{linktr.ee/pkawak}
\end{center}

\section*{Professional Summary}

Computational polymer physicist specializing in molecular simulation, polymer physics, and statistical mechanics, with extensive experience leading collaborative projects across materials science, chemical engineering, and soft matter.
\vspace{0.5em}

\begin{tabitemize}[leftmargin=*]
    \item Design, optimize, and deploy large-scale molecular dynamics and Monte Carlo workflows (LAMMPS, GROMACS, HOOMD-blue; C++/Python/CUDA) to uncover structure–property relationships in polymers and soft materials.
    \item Lead cross-functional research teams, mentoring graduate and undergraduate researchers in molecular simulation, HPC workflows, software practices, and scientific communication.
    \item Architect and accelerate high-throughput analysis pipelines for polymer simulations, including profiling and optimizing in-house codes in Python, C++, and CUDA for multi-node CPU/GPU environments.
    \item Translate nanoscale insights into design rules for tough, recyclable, and sustainable materials, including elastomeric nanocomposites and sequence-defined copolymers.
    \item Maintain a strong record of technical communication and leadership through peer-reviewed publications, invited talks, and organization of professional development events, research symposia, and training sessions and workshops.
\end{tabitemize}

\section*{Technical Skills}

\begin{tabitemize}[leftmargin=*]
    \item \textbf{Simulation and Modeling:} Molecular dynamics (MD), Monte Carlo (MC), advanced sampling algorithms (e.g., Wang–Landau, configurational bias), coarse-grained and atomistic modeling, non-equilibrium simulations, phase behavior analysis, and free energy calculations; experience with LAMMPS, GROMACS, HOOMD-blue, and custom C++/CUDA engines.
    \item \textbf{Software Development:} Architecting, profiling, and maintaining scientific software in Python, C, C++, CUDA, Bash, Julia, R, Matlab, and FORTRAN; collaborative development with Git (branching, pull requests, code review), unit testing, and continuous integration / continuous deployment (CI/CD).
    \item \textbf{Analysis and Data Processing:} Custom analysis pipelines for molecular simulation data using Python (NumPy, SciPy, Matplotlib, Pandas, scikit-learn), Bayesian optimization, statistical modeling, bash scripting, and parallel computation (MPI, CUDA, SLURM).
    \item \textbf{High-Performance Computing:} Experience with HPC job scheduling (SLURM), distributed computing with MPI, GPU-accelerated computing (CUDA, Nsight, nvprof, nvidia-smi), and large-scale runs on university and national supercomputing resources.
    \item \textbf{Debugging and Profiling:} GDB, valgrind, callgrind, perf, Nsight, nvprof, nvidia-smi; diagnosing memory leaks, race conditions, and performance bottlenecks in C++/Python/CUDA codebases.
    \item \textbf{Data Management and Visualization:} Terabyte-scale data handling, automated backups and compression; visualization with Matplotlib, VMD, OVITO, and Inkscape for publication-quality figures.
    \item \textbf{Process Simulation and Thermodynamics:} Experience with process simulation tools (Aspen HYSYS) and thermodynamic modeling in chemical engineering contexts.
    \item \textbf{Leadership and Communication:} Leading research teams, mentoring junior researchers, organizing training sessions, professional development workshops and symposia; scientific writing (8 peer-reviewed publications) and technical presentations (28 talks).
\end{tabitemize}

\section*{Research Experience}

\textbf{Postdoctoral Researcher}, University of South Florida \hfill \textit{2022 – Present} \\
\textit{Advisor: Prof.~David Simmons}
\vspace{0.5em}

\textbf{Material Simulation and Analysis}
\begin{tabitemize}[leftmargin=*]
    \item Developed large-scale molecular dynamics simulations to investigate void formation, failure, and nanoscale reinforcement mechanisms in elastomeric nanocomposites.
    \item Simulated thermo-elastoplastic deformation and rheology of filled rubber systems, linking nanoscale structure and interfacial physics to macroscopic stress–strain response.
    \item Automated selection, generation, and testing of atomistic models for sequence-designed copolymers to probe glass transition behavior and thermal stability.
    \item Identified copolymer sequences with enhanced glass transition temperatures without altering processing or feedstock chemistry, informing experimental design.
    \item Applied Bayesian optimization and statistical modeling to fit relaxation dynamics and extract glass transition behavior from noisy, high-dimensional simulation data.
    \item Led multi-dimensional parameter sweeps (nanoparticle size, chemistry, volume fraction) to optimize nanocomposite designs.
    \item Collaborated with experimentalists to validate molecular predictions against thermal and mechanical performance targets, closing the loop between simulation and experiment.
    \item Conceived and led multiple projects from idea to peer-reviewed manuscripts within 2–6 months each, driving rapid cycles of hypothesis generation, replication, and analysis.
    \item Developed methods to extract stress hotspots from 3D trajectories for identifying mechanisms of reinforcement.
\end{tabitemize}

\vspace{0.5em}
\textbf{Software Development and Automation}
\begin{tabitemize}[leftmargin=*]
    \item Architected Python/C++/CUDA simulation and analysis toolchains to enable high-throughput, physics-informed property prediction across diverse polymer systems.
    \item Developed modular rheology, thermal, and structural analysis toolkits integrated into lab-wide workflows, improving reproducibility and reusability of analysis code.
    \item Automated data analysis pipelines handling 100+ TB of simulation data, reducing turnaround time by \textasciitilde 90\% through batching, caching, and parallel execution.
    \item Built Bash, SLURM, and MPI automation scripts for large-scale HPC job orchestration, checkpointing, restart logic, and robust recovery from node and queue failures.
    \item Modernized a 50k+ line legacy C++ molecular dynamics analysis toolkit (AMDAT) into a modular, version-controlled, and tested codebase, introducing Git workflows and issue tracking.
    \item Open-sourced AMDAT on GitHub with CI/CD, unit tests, and comprehensive user/developer documentation, enabling external researchers to analyze LAMMPS and GROMACS trajectories at scale.
    \item Designed and launched AMDAT documentation and example-driven tutorials, significantly lowering onboarding time for new users and collaborators.
\end{tabitemize}

\vspace{0.5em}
\textbf{High-Performance Computing and Workflow Acceleration}
\begin{tabitemize}[leftmargin=*]
    \item Led optimization of 50+ TB data pipelines across HPC clusters, improving data throughput by \textasciitilde 90\% and reducing wall-clock time for key workflows from weeks to days.
    \item Architected scalable storage and compression pipelines for long-running simulations, improving data access patterns and long-term reproducibility across projects.
    \item Streamlined multi-node CPU and GPU workflows for molecular simulations, including job arrays, dependency graphs, and automated resource selection.
    \item Reduced simulation runtime by up to 90\% through parallelization, GPU acceleration, and high-performance computing resource optimization.
    \item Secured NSF ACCESS compute resources to support scalable, HPC-enabled molecular simulation campaigns.
\end{tabitemize}

\vspace{0.5em}
\textbf{Debugging, Profiling, and Performance Tuning}
\begin{tabitemize}[leftmargin=*]
    \item Debugged and profiled C++/Python codebases using GDB, valgrind, callgrind, perf, Nsight, nvprof, and nvidia-smi, resolving memory leaks and runtime bottlenecks.
    \item Improved software modularity, runtime, and scalability for multi-month, high-dimensional simulations by refactoring core data structures and algorithms.
    \item Established best practices for code maintainability and scalability through internal documentation, technical presentations, and example-driven refactors.
\end{tabitemize}

\vspace{0.5em}
\textbf{Leadership, Mentorship, and Community Engagement}
\begin{tabitemize}[leftmargin=*]
    \item Led and mentored 10+ researchers in HPC workflows, molecular simulation, version control, and scientific computing practices, serving as a go-to technical resource in the group.
    \item Designed structured onboarding programs, documentation, and tutorials to train new users on simulation workflows, AMDAT, and lab software standards.
    \item Drove the group-wide transition to modern software practices around AMDAT and related toolchains, including Git-based workflows, code review, and documentation culture.
    \item Organized and contributed to training sessions and internal workshops on simulation methods, HPC usage, and reproducible research practices.
    \item Delivered 20+ technical presentations at internal, academic, and industrial venues, including award-winning talks at major conferences.
\end{tabitemize}

\textbf{Ph.D.~Researcher}, Brigham Young University \hfill \textit{2017 – 2022} \\
\textit{Advisor: Prof.~Douglas Tree}

\vspace{0.5em}
\textbf{Software Development and GPU Acceleration}
\begin{tabitemize}[leftmargin=*]
    \item Built two GPU-accelerated Monte Carlo engines in C++/CUDA ($\sim$ 80,000 lines) to simulate polymer crystallization and free-energy landscapes, with modular data structures and reusable kernels.
    \item Implemented advanced sampling algorithms (e.g., configurational bias, Wang–Landau) to efficiently explore high-dimensional molecular states and rare events.
    \item Solved critical convergence failures in polymer crystallization simulations by architecting a scalable, GPU-accelerated multi-window Monte Carlo framework — cutting runtimes from weeks to hours and enabling previously impossible sampling.
    \item Designed a multi-window, multi-walker sampling framework with checkpointing and automatic load balancing across GPUs/CPUs, enabling tractable modeling of metastable and glassy states.
    \item Optimized GPU kernels (e.g., cell lists, neighbor search, reductions) for occupancy and memory coalescing, achieving 100$\times$ speedups over CPU-only implementations.
    \item Used NVIDIA profiling tools (Nsight, nvprof, nvidia-smi) and standard debuggers (GDB, valgrind) to diagnose performance bottlenecks and numerical issues in GPU-accelerated codes.
\end{tabitemize}

\vspace{0.5em}
\textbf{Structure–Property Analysis and Data Processing}
\begin{tabitemize}[leftmargin=*]
    \item Developed numerical algorithms to quantify nanoscale crystalline and orientational order from 3D simulation trajectories, supporting automated detection of polymorphs and defects.
    \item Built Python-based analysis pipelines (NumPy, SciPy, Pandas, Matplotlib) to process large simulation datasets into free-energy profiles, phase diagrams, and thermodynamic response functions.
    \item Automated parameter sweeps and post-processing to extract structure–property relationships, reducing manual analysis time and standardizing data products across projects.
\end{tabitemize}

\vspace{0.5em}
\textbf{High-Performance Computing and Workflow Optimization}
\begin{tabitemize}[leftmargin=*]
    \item Leveraged university and national HPC clusters (SLURM, MPI) to perform long-timescale, high-throughput Monte Carlo simulations over large parameter spaces.
    \item Automated multi-parameter simulation campaigns with job arrays, dependency graphs, and robust restart logic, reducing wall-clock time for full phase-diagram calculations from weeks to days.
    \item Implemented systematic logging, data organization, and compression workflows to ensure reproducibility and efficient reuse of multi-terabyte simulation datasets.
    \item Led development of a multi-walker, multi-window parallel sampling architecture deployed across 320+ concurrent jobs, integrating CPU/GPU scheduling and inter-process communication to boost sampling ergodicity and simulation throughput.
    \item Implemented fail-safe heartbeat system for resilient simulation orchestration and dynamic restart logic in long-timescale jobs.
    \item Built an automated, robust, and modular Python workflow system with JSON-based simulation state tracking, adaptive resource allocation, and dynamic error handling across SLURM-managed HPC jobs.
\end{tabitemize}

\vspace{0.5em}
\textbf{Scientific Communication and Collaboration}
\begin{tabitemize}[leftmargin=*]
    \item Co-authored peer-reviewed publications and multiple conference presentations on polymer crystallization and nanoscale structure.
    \item Mentored 4 undergraduate researchers in C++/Python programming, HPC workflows, and scientific analysis, with several mentees progressing to graduate research roles.
    \item Provided key simulation results and software infrastructure that contributed to a successful \$500,000 NSF CAREER proposal on polymer crystallization.
  \item Won APS Distinguished Student Award and BYU Research Presentation Award.
\end{tabitemize}

\textbf{Graduate Researcher}, American University of Sharjah \hfill \textit{2015 – 2017} \\
\textit{Advisor: Prof.~Ghaleb Husseini}
\begin{tabitemize}[leftmargin=*]
  \item Developed estrone-functionalized drug nanocarriers for targeted breast cancer chemotherapy, coordinating synthesis, characterization, and in vitro testing.
  \item Optimized ultrasound-triggered drug release by systematically varying acoustic parameters to tune release profiles for chemotherapy applications.
  \item Characterized nanocarrier size, stability, and drug loading using NMR and dynamic light scattering to ensure reproducible and therapeutically relevant formulations.
  \item Standardized experimental protocols and data-recording workflows, improving reproducibility and enabling consistent results across collaborators.
  \item Presented findings at 3 conferences, including a Best Talk award at the AUS Biomedical Symposium.
\end{tabitemize}

\section*{Leadership and Community Engagement}
\begin{tabitemize}[leftmargin=*]
  \item \textbf{Founder \& Chair}, USF Postdoctoral Scholar Association Executive Committee (2023–Present) \\
        Established and lead an organization representing \textasciitilde 200 postdocs; coordinate professional development programming, social events, and communication with university leadership, including the NPA-funded ELEVATE Talk Series.
  \item \textbf{Co-founder \& President}, BYU Chemical Engineering Graduate Student Council (2018–2021) \\
        Launched a graduate council to improve communication, recruitment, and community; organized department-wide events and conducted surveys on financial well-being to inform departmental decisions.
  \item \textbf{Administrator}, Early Career Researchers in Polymer Physics Network (2021–Present) \\
        Manage an international Slack community of 500+ early-career researchers; coordinate virtual events such as a 150+ attendee Virtual Polymer Physics Symposium and ongoing peer networking.
  \item \textbf{Scholarship Coordinator \& Mentor}, oSTEM (2022–Present) \\
        Lead review of 200+ scholarship applications per cycle and mentor early-career scientists and engineers through structured mentoring programs.
  \item \textbf{STEM Outreach and Judging} \\
        Contributed to outreach and talent pipeline development via classroom visits, seminar-style workshops for high school and college students, and judging at regional and state science fairs.
\end{tabitemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Articles and Presentations %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%recompile from start if numbers aren't right
\begin{refsection}[articles]
  \nocite{*}
  \setlength\bibitemsep{0pt}
  \printbibliography[resetnumbers=true,type=article,title={Selected Peer-Reviewed Publications},heading=fix]
\end{refsection}
\noindent\textit{Full list of publications and presentations available at \href{https://linktr.ee/pkawak}{linktr.ee/pkawak}}

\section*{Education}
\textbf{Ph.D.} in Chemical Engineering, Brigham Young University \hfill \textit{2022} \\
\textbf{M.S.} in Chemical Engineering, American University of Sharjah \hfill \textit{2017} \\
\textbf{B.S.} in Chemical Engineering (Econ.~Minor), American University of Sharjah \hfill \textit{2015}

%\vspace{-0.3\baselineskip}

\end{document}
